network_plot

### 2024-02-09 R/run_first/2.plot_pathway_net_example.Rmd
renv

type <- V(g)$name
```

```{r}
id <- c(1:length(type))

@@

type[which(type %in% baits)] <- "POI"
type[which(type %in% spikes)] <- "RP"

type[-which(type %in% c("POI","RP"))] <- "URP"

@@

Baits <- names(V(g))
Baits[-which(Baits %in% temp)] <- "Other"
Baits[which(Baits %in% temp)] <- "baits"

@@

tidynet <- tidynet %>%
  activate(nodes) %>%
  mutate(type = type)

tidynet <- tidynet %>%
  activate(nodes) %>%
  mutate(Baits = Baits)

@@

realplot <- ggraph(tidynet, layout = coords) + 
  geom_edge_link(aes(colour = association, alpha = weight), show.legend=FALSE) +  
  scale_edge_color_manual(values = edge_colours, guide = "none") +
  geom_node_point(
    aes(size = VIP, color = type, shape = Baits), show.legend=FALSE         #CHANGE THIS
  ) +
  geom_node_point(
    aes(color = type)    #, shape = Baits
  ) +
  scale_color_manual(values = colours) + 
    scale_shape_manual(values = c(17,16)) +   #18,20

@@

adj[type == "URP", type == "URP"]  <- 1
adj[type %in% c("POI","RP"), type %in% c("POI","RP")] <- 1

adj[type %in% c("POI","RP"), type == "URP"] <- -1
adj[type == "URP", type %in% c("POI","RP")] <- -1
```

@@

#define correctly ordered type type
type <- V(g)$name

@@

```{r}
id <- c(1:length(type))

@@

tidynet <- tidynet %>%
  activate(nodes) %>%
  mutate(type = type)

@@

badplot <- ggraph(tidynet, layout = coords) + 
  geom_edge_link(aes(colour = association, alpha = weight), show.legend=FALSE) +   #, linetype = "dashed"
  scale_edge_color_manual(values = edge_colours, guide = "none") +
  geom_node_point(
    aes(size = VIP, color = type, shape = Baits), show.legend=FALSE
  ) +
  geom_node_point(
    aes(color = type)
  ) +
  scale_color_manual(values = colours) + 
      scale_shape_manual(values = c(17,16)) +   #18,20
  # scale_edge_linetype_manual(values = "dashed") +

>>>>

Net <- V(g)$name
```

```{r}
id <- c(1:length(Net))

@@

Net[which(Net %in% baits)] <- "POI"
Net[which(Net %in% spikes)] <- "RP"

Net[-which(Net %in% c("POI","RP"))] <- "URP"

@@

Gene <- names(V(g))
Gene[-which(Gene %in% temp)] <- "Other"
Gene[which(Gene %in% temp)] <- "Baits"

@@

tidynet <- tidynet %>%
  activate(nodes) %>%
  mutate(Net = Net)

tidynet <- tidynet %>%
  activate(nodes) %>%
  mutate(Gene = Gene)

@@

realplot <- ggraph(tidynet, layout = coords) + 
  geom_edge_link(aes(colour = association, alpha = weight), show.legend=FALSE) +  
  scale_edge_color_manual(values = edge_colours, guide = "none") +
  geom_node_point(
    aes(size = VIP, color = Net, shape = Gene), show.legend=FALSE        #CHANGE THIS
  ) +
  geom_node_point(
    aes(color = Net, shape = Gene)    #, shape = Baits
  ) +
  scale_color_manual(values = colours) + 
    scale_shape_manual(values = c(17,16)) +   #18,20

@@

adj[Net == "URP", Net == "URP"]  <- 1
adj[Net %in% c("POI","RP"), Net %in% c("POI","RP")] <- 1

adj[Net %in% c("POI","RP"), Net == "URP"] <- -1
adj[Net == "URP", Net %in% c("POI","RP")] <- -1
```

@@

#define correctly ordered type Net
Net <- V(g)$name

@@

```{r}
id <- c(1:length(Net))

@@

tidynet <- tidynet %>%
  activate(nodes) %>%
  mutate(Net = Net)

@@

badplot <- ggraph(tidynet, layout = coords) + 
  geom_edge_link(aes(colour = association, alpha = weight), show.legend=FALSE) +   #, linetype = "dashed"
  scale_edge_color_manual(values = edge_colours, guide = "none") +
  geom_node_point(
    aes(size = VIP, color = Net, shape = Gene), show.legend=FALSE
  ) +
  geom_node_point(
    aes(color = Net, shape = Gene)
  ) +
  scale_color_manual(values = colours) + 
      scale_shape_manual(values = c(17,16)) +   #18,20
  # scale_edge_linetype_manual(values = "dashed") +
